Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations

### 2020-12-31 paper.Rnw
typos

While the concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}. The current implementations of LIME \citep{pedersen:2020, ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation. Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation. In order to achieve reasonable  explanations, the tuning parameter values selected shoud  be assessed.

@@

Recall,  \autoref{fig:figure-04} shows  the kernel density method returns the same explanations  across all cases in the test set suggesting a global trend may be the best explanation for this example. This may be reasonable considering that we would expect  $x_1$ and $x_2$ to be  the two features  used by the random forest to distinguish between response categories. However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.

>>>>

While the concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}. The current implementations of LIME \citep{pedersen:2020, ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation. Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation. In order to achieve reasonable  explanations, the tuning parameter values selected should  be assessed.

@@

Recall,  \autoref{fig:figure-04} shows  the kernel density method returns the same explanations  across all cases in the test set suggesting a global trend may be the best explanation for this example. This may be reasonable considering that we would expect  $x_1$ and $x_2$ to be  the two features  used by the random forest to distinguish between response categories. However, further exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
